SVG: The Paper

### 2022-06-07 Analysis/index.Rmd
init sel post pred

# Item Density

>>>>

## Posterior Predictions

```{r}
gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
  group_by(c, .variable) %>%
  summarise(value = mean(.value)) %>%
  pivot_wider(names_from = ".variable", values_from = "value") -> am

c1 <- filter(am, c==1)
c2 <- filter(am, c==2)

gather_draws(m, lambda[observer]) %>%
  group_by(observer, .variable) %>%
  summarise(value = mean(.value)) %>%
  select(-.variable) -> lambdas

  lambda <- filter(lambdas, observer == obs)$value

  wx <- lambda * dbeta(dt$x, c1$a_x, c1$b_x) +
    (1-lambda) * dbeta(dt$x, c2$a_x, c2$b_x)

  wy <- lambda * dbeta(dt$y, c1$a_y, c1$b_y) +
    (1-lambda) * dbeta(dt$y, c2$a_y, c2$b_y)

  w <- wx * wy
  w <- w / sum(w)

d %>% group_by(observer, condition, trial) %>%
  summarise(n = n(), .groups = "drop") %>%
  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
  pmap_df(get_model_weight) -> weights2

bind_rows(weights %>% mutate(method = "multi-level"), 
          weights2 %>% mutate(method = "mixture model")) -> dw

ggplot(dw, aes(init_weight, fill = method)) + 
  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1)) %>%
  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") -> plt2

weights2 %>% group_by(observer) %>%
  summarise(accuracy = mean(max_item == 1)) %>%
  full_join(lambdas) %>%
  rename(lambda = "value") %>%
  ggplot(aes(lambda, accuracy)) + 
  geom_point() +
  geom_smooth(method = "lm", colour = "black") -> plt3

plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")

dw %>% group_by(method, observer) %>%
  summarise(score = median(init_weight),
            accuracy = mean(max_item==1)) %>%
  summarise(mean_score = mean(score),
            mean_accuracy = mean(accuracy)) %>%
  knitr::kable()
